\documentclass[10pt]{article}
\usepackage[vmargin=1cm, hmargin=1cm]{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{pdflscape}
\begin{document}

\begin{landscape}
\begin{longtable}[]{llp{1.5cm}p{2cm}p{2.5cm}llp{2.5cm}}
\toprule
Resource & URI Scheme & Properties & Links & GET & PUT & DELETE & POST\tabularnewline
\hline
\midrule
\endhead

students & /student &  & students & Student Links & N/A & N/A & Add student?\tabularnewline
\hline

student & /student/\{login\} & login first last & enrollments & Student info. enrollment links & Create? Replace? & Delete & Update info name\tabularnewline
\hline

enrollment & /enrollment/\{section\}/\{login\} & responded & student section & Is enrolled? & Enroll student & Remove student & N/A\tabularnewline
\hline

roster & /enrollment/\{section\} &  & enrollments section & Class roster &  & N/A & Mass enroll?\tabularnewline
\hline

instructors & /instructor &  & active instrs & Active instrs & N/A & N/A & Add instr?\tabularnewline
\hline

instructor & /instructor/\{login\} & first last & sections dept & Instructor info & Create? Replace? & Remove? & Update name\tabularnewline
\hline

admins & /admin &  & admins & Admin list & N/A & N/A & Add admin?\tabularnewline
\hline

an admin & /admin/\{login\} & first last &  & ????? & Create? Replace? & Remove & Update info\tabularnewline
\hline

terms & /term &  & terms & terms list & N/A & N/A & Add term?\tabularnewline
\hline

term & /term/\{year\}/\{period\} & dates & year period sections & term info sections year, period & New term? & Remove? & Update dates\tabularnewline
\hline

depts & /dept &  & depts divisions? & dept links & N/A & N/A & Add dept?\tabularnewline
\hline

a dept & /dept/\{prefix\} & name & head members parent tags & dept info & Create? & Remove? & Update what?\tabularnewline
\hline

courses & /course &  & courses & course list depts? & N/A & N/A & Add course?\tabularnewline
\hline

a course & /course/\{prefix\}/\{id\} & descr no & dept sections tags parent & course info dept sections tags & Create? & Remove? & Update info\tabularnewline
\hline

sections & /section &  & sections & section list & N/A & N/A & Add section?\tabularnewline
\hline

a section & /section/\{year\}/\{term\}/\{no\} & state & course roster year term & section info & Create? & Remove? & Update info?\tabularnewline
\hline

tags & /tag &  & tags & links to tags & N/A & N/A & Create new tag?\tabularnewline
\hline

a tag & /tag/\{tag\} & descr? & questions depts? courses? sections? & tag info questions? & Create? & Delete? & Change descr? Change questions?\tabularnewline
\hline

questions & /tag/\{tag\}/question &  & questions & ordered questions & N/A & N/A & Add question. order?\tabularnewline
\hline

question & /tag/\{tag\}/question/\{id\} & type prompt & choices & question info & N/A & Remove? & Update question. order? choices?\tabularnewline
\hline

answers? &  &  &  &  &  &  & \tabularnewline
\hline

evals? &  &  &  &  &  &  & \tabularnewline
\hline
\bottomrule
\end{longtable}
\end{landscape}
\end{document}
